### 2012-07-04 inst/examples/Reed.Rmd
Reed debug (cost = 0)

``` {r }
pars <- c(A, B)
````

@@

``` {r  profit}
price <- 1
c0 <- 5
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r  }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn2)
````

@@

``` {r  find_dp_optdet }
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r cleanup}
options(device=orig)
````

>>>>

``` {r }
pars <- c(A, B)
K <- (A-1)/B
````

@@

``` {r  profit}
price <- 1
c0 <- 0
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

``` {r  }
SDP_Mat2 <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn)
````

@@

``` {r  find_dp_optdet }
det <- find_dp_optim(SDP_Mat2, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@
